\documentclass[a4paper,11pt]{beamer}
\useoutertheme{shadow} 
\usetheme{Berkeley}

\usepackage{times}

\makeatletter

\setbeamertemplate{sidebar \beamer@sidebarside}%{sidebar theme}
{
	\beamer@tempdim=\beamer@sidebarwidth%
	\advance\beamer@tempdim by -6pt%
	\insertverticalnavigation{\beamer@sidebarwidth}%
	\vfill
	\ifx\beamer@sidebarside\beamer@lefttext%
	\else%
	\usebeamercolor{normal text}%
	\llap{\usebeamertemplate***{navigation symbols}\hskip0.1cm}%
	\vskip2pt%
	\fi%
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add page number
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\raisebox{1.2pt}[0pt][0pt]{\insertframenumber/\inserttotalframenumber}
}

\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Set Title, Author and date 
\title[Short Title]{Title Page Title}
\author[Short Author]{Title Page Author}
\date{1980 02 29}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page
	\begingroup
	\makeatletter
	\setlength{\hoffset}{-.5\beamer@sidebarwidth}
	\makeatother
	\begin{frame}[plain]
		\titlepage
	\end{frame}
	\endgroup
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sections
\section{Section 1}
\subsection{Subsection 1}
\subsubsection{Subsubsection 1-1}

	\begin{frame}{Frame Name}{Frame Subname}
		When life gives you lemons, don't make lemonade. Make life take the lemons back! Get mad! I don't want your damn lemons, what the heck am I supposed to do with these? Demand to see life's manager! Make life rue the day it thought it could give Cave Johnson lemons! Do you know who I am? I'm the man who's gonna burn your house down! With the lemons! I'm gonna get my engineers to invent a combustible lemon that burns your house down!
	\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Columns in frame
\subsection{Subsection 2}
\subsubsection{Subsubsection 2-1}

	\begin{frame}{Columns}
		\begin{columns}
			\begin{column}{.2\textwidth}
				1st column 0.2 textwidth
			\end{column}
			\begin{column}{.3\textwidth}
				2nd column 0.3 textwidth
			\end{column}
			\begin{column}{.5\textwidth}
				3rd column 0.5 textwidth
			\end{column}
		\end{columns}
	\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Columns in multiple line
\subsubsection{Subsubsection 2-2}

	\begin{frame}{Columns}{Columns in multiple line}
		\begin{columns}
			\begin{column}{.4\textwidth}
				a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
			\end{column}
			\begin{column}{.6\textwidth}
				b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b b
			\end{column}
		\end{columns}
		\vspace{.5cm}
		\begin{columns}
			\begin{column}{.6\textwidth}
				c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c c 
			\end{column}
			\begin{column}{.4\textwidth}
				d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d d
			\end{column}
		\end{columns}
	\end{frame}

\end{document}